Statistical Geometry of the turbulent ISM - I. Field lines

### 2015-01-11 field_lines/mhdruns.tex

  The total volume probability distributions for gas number density $n$, 
  temperature $T$ and thermal pressure $p$ are displayed in Fig.~\ref{fig:pdfm}
  from Models~$\Ompa$ (black, solid) and $\Omph$ (blue, dashed). 
  Note that Model~$\Omph$ includes the correction to the SN distribution,
  which stabilises the disc against unphysical cyclic oscillations, although
  it is still subject to natural random vertical fluctuations.
  Hence the mean density in the SN active region remains consistently higher
  than in Model~\Op.

%-----------------------------------------------------------------------------
  \begin{figure}[h]
  \centering\hspace{-2cm}
  \includegraphics[width=0.36\columnwidth,clip=true,trim=0 0 0 9mm]{fig/o1pr_rpdf.png}
  \includegraphics[width=0.36\columnwidth,clip=true,trim=0 0 0 9mm]{fig/o1pr_tpdf.png}
  \includegraphics[width=0.36\columnwidth,clip=true,trim=0 0 0 9mm]{fig/o1pr_ppdf.png}
  \hspace{-2cm}
    \caption[Total volume probability distributions for Model~$\Ompa$ and $\Omph$]{
  Volume weighted probability distributions of gas number
  density~{\textbf{(a)}}, temperature~{\textbf{(b)}} and thermal
  pressure~{\textbf{(c)}} for  models {$\Omph$} (black, solid) and
  {$\Ompa$} (blue, dashed) for the total numerical domain $|z|\le1.12\kpc$.
    \label{fig:pdfm}}
  \end{figure}
%-----------------------------------------------------------------------------

  Although the three phase temperature distribution is still visible for this
  model in Fig.~\ref{fig:pdfm}b, it is less pronounced than the results from
  Model~\Op\ shown in Fig.~\ref{fig:pdf2}b.
  However the three phase structure for the MHD Model~$\Ompa$ is not at all
  apparent in panel b, with a significantly narrower range of temperatures.
  The bulk of the density distributions (a) are quite similar between the 
  HD and MHD models, except that the high densities are not as well resolved in
  the MHD models.
  The thermal pressure distributions are very similar, but with the HD modal
  pressure approximately one third the MHD modal pressure.

%-----------------------------------------------------------------------------
  \begin{figure}[h]
  \centering\hspace{-2cm}
  \includegraphics[width=0.535\columnwidth]{fig/zrhom.png}
  \includegraphics[width=0.535\columnwidth]{fig/zrppm.png}\hspace{-2cm}
    \caption[Horizontal averages of $n$ and $P$ for Model~$\Ompa$ and $\Omph$]{
  Horizontal averages of gas number density, $\mean{n}(z)$ {\textbf{(a)}}, and
  total pressure, $\mean{P}(z)$ {\textbf{(b)}}, for Model~{$\Ompa$} (solid,
  black), and Model~{$\Omph$} (dashed, blue). 
  Each are time-averaged using eleven snapshots respectively, spanning 
  100\Myr.
  The vertical lines indicate standard deviation within each horizontal slice.
  The thermal $\mean{p}(z)$ (dotted) and ram $\mean{p}\turb(z)$ (fine dashed)
  pressures are also plotted {\textbf{(b)}}.
  For Model~{\OpH} the magnetic pressure $\mean{p}_B$ is also plotted (fine, 
  dash-3dotted).
    \label{fig:zrhom}
            }
  \end{figure}
%-----------------------------------------------------------------------------

  As discussed in Section~\ref{subsect:params} the stability of the disc
  reduces the effectiveness of the SNe to generate and circulate hot gas, in
  the absence of SN clustering. 
  Hence Model~$\Omph$ has a slightly thicker disc, with less hot gas than 
  Model~\Op.
  On top of this the effect of the magnetic pressure in Model~$\Ompa$ is to 
  expand the thick disc even further and this is illustrated in 
  Fig.~\ref{fig:zrhom}a, where the horizontal averages of gas number density
  $n(z)$ are plotted against $z$ for both models. 
  The strong peak in the density at the mid-plane is evident for Model~$\Omph$
  (black, solid), while for Model~$\Ompa$ (blue, dashed) there is a broad
  plateau in the density, extending to $|z|\simeq300\pc$, where the mean 
  magnetic field is strongest.

%-----------------------------------------------------------------------------
  \begin{figure}[h]
  \centering
  \includegraphics[width=0.45\linewidth]{fig/o1pr_npdf3s.png}  
  \includegraphics[width=0.45\linewidth]{fig/o1ph_npdf3s.png}\\  
  \includegraphics[width=0.45\linewidth]{fig/o1pr_tpdf3s.png}
  \includegraphics[width=0.45\linewidth]{fig/o1ph_tpdf3s.png}  
    \caption[Probability distributions by phase for $n$ and $T$]{
  Probability distributions by phase: cold (blue, dashed), warm (black, solid)
  and hot (red, dash-dotted) for gas number density ($n$ {\textbf{(a), (b)}})
  and temperature ($T$ {\textbf{(c), (d)}}) 
  for Model~$\Ompa$ ({\textbf{(a), (c)}}) and Model~$\Omph$
  ({\textbf{(b), (d)}}).
%  Data are averaged over 100\,Myr using eleven snapshots. 
  95\% confidence intervals for temporal deviation are shown as error bars.   
  \label{fig:npdf3s}
    }
  \end{figure}
%-----------------------------------------------------------------------------

  The horizontal averages of the pressure are plotted in Fig.~\ref{fig:zrhom}b
  for both models. 
  There is a strong peak at the mid-plane in the turbulent pressure for the HD
  model (black, dashed), but a much weaker profile for the MHD model (blue,
  dash-dotted). 
  There are two peaks in the magnetic pressure (blue, dash-3dotted) near 
  $|z|\simeq200\pc$, which supports the extended density profile.
  Another possible effect, which might constrain the circulation of the hot
  gas, and hence enhance the pressure at the mid-plane, is the strong 
  horizontal orientation of the field.
  As mentioned in Section~\ref{sect:dyn} the periodic boundary conditions
  exclude a non-zero vertical component to the mean field, so the magnetic
  tension predominantly acts against the vertical flows.
  Some understanding of the multi-phase structure of the magnetised ISM is
  still possible from these models, but the extreme temperatures and densities
  are significantly under represented.
  To improve this in future work it will be desirable to allow unrestricted 
  evolution of vertical field and to apply realistic clustering of the 
  SNe to generate more supperbubbles (composite multiple SN remnants forming a
  single superstructure) or chimneys (plumes venting hot gas from the disc 
  towards the halo).

  Results for separation of the ISM into three phases using the method 
  detailed in Section~\ref{sect:entropy} are shown for Models~$\Ompa$ and
  $\Omph$ in Fig~\ref{fig:npdf3s} with total volume probability distributions.
  The phases are defined using entropy $s$ such that for cold 
  $s<4.4\cdot10^{8}\erg \g^{-1}\K^{-1}$ and hot 
  $s>23.2\cdot10^{8}\erg \g^{-1}\K^{-1}$ with warm in between.
  Apart from the higher densities for the cold phase with the HD model (panel 
  b), 
  anticipated by the volume distributions (Fig.~\ref{fig:pdfm}), the warm and
  hot distributions for the MHD density (panel a) are broad, with a bimodal 
  structure to the hot gas. 
  The distributions for the warm gas (panels c and d) are very similar and for the
  cold (hot) distributions the MHD model does not extend to as low (high)
  temperatures.

%-----------------------------------------------------------------------------
  \begin{figure}[h]
  \centering
  \includegraphics[width=0.475\linewidth]{fig/o1pr_pdf2dtn.png}  
  \includegraphics[width=0.475\linewidth]{fig/o1ph_pdf2dtn.png}
    \caption[2D probability distribution of $n$ and $T$ for Models~$\Ompa$ and $\Omph$]{
  Probability contour plot by volume of log$n$ vs log$T$ for Model~$\Ompa$
  {\textbf{(a)}}
  and Model~$\Omph$ {\textbf{(b)}}.
  The lines of constant entropy $s=4.4\cdot10^{8}$ 
  and $23.2\cdot10^{8}\erg\g^{-1}\K^{-1}$ indicate where the phases are defined
  as cold for $s\le4.4$ and as hot for $s>23.2$. 
  \label{fig:b2dv}
    }
  \end{figure}
%-----------------------------------------------------------------------------

  Comparing the combined probability distribution of density and temperature
  for both of these models in Fig.~\ref{fig:b2dv} with those of Model~\Op\
  in Fig.~\ref{fig:pdf2d} the spread is more broad and not obviously 
  aligned along a line of constant pressure.
  The HD distribution here is less compact than with MHD. 
  However when considering only the mid-plane distributions, as displayed in
  Fig.~\ref{fig:b2dh} the distributions match better with Model~\Op\ and the 
  pressure alignment is evident.
  So the broad distributions for the total volumes are explained by the 
  stronger gradient in the pressure distribution, due to the reduced 
  stirring of the hot gas.
  The thermal pressure at the mid-plane is also very similar in both models,
  reflected also in the agreement of the total and thermal pressure near the
  mid-plane in the plot of horizontal averages (Fig~\ref{fig:zrhom}b).
  The magnetic and turbulent pressure in Model~$\Ompa$ combine to match the
  mid-plane turbulent pressure alone of Model~$\Omph$.
  For the temperature in Model~$\Ompa$ the hot gas has two modes, evident in 
  Fig.~\ref{fig:b2dv}a at $10^5\K$ and $10^6\K$, but at the mid-plane there 
  only the single $10^3\K$ mode. 
  The structure of the ISM at the mid-plane is therefore common to both models
  with modes at $10^6\K,~10^{-2}\cmcube$ and $10^4\K,~1\cmcube$.
  The cold gas is insufficiently resolved in Model~$\Ompa$ for comparison.

%-----------------------------------------------------------------------------
  \begin{figure}[h]
  \centering
  \includegraphics[width=0.475\linewidth]{fig/o1pr_pdf2dh.png}  
  \includegraphics[width=0.475\linewidth]{fig/o1ph_pdf2dh.png}
    \caption[2D mid-plane probability distribution for Models~$\Ompa$ and  $\Omph$]{
  The mid-plane probability distributions ($|z|<100\pc$) by gas number density 
  $\log n$ and temperature $\log T$ for {\textbf{(a)}} Model~$\Ompa$ and
  {\textbf{(b)}} Model~$\Omph$.
  \label{fig:b2dh}
    }
  \end{figure}
%-----------------------------------------------------------------------------

@@

%-----------------------------------------------------------------------------
  \begin{figure}[h]
  \centering
  \includegraphics[width=0.475\linewidth]{fig/o1pr_pdf2db.png}  
  \includegraphics[width=0.475\linewidth]{fig/o1pr_pdf2tb.png}
    \caption[2D probability distribution of $n,B$ and $B,T$ for Model~$\Ompa$]{
  Total volume probability distributions ($|z|<100\pc$) by gas number density 
  $\log n$ and magnetic field strength $\log |B|$ {\textbf{(a)}} and
  temperature $\log |T|$ and magnetic field strength $\log |B|$ 
  {\textbf{(b)}} for Model~$\Ompa$.
  \label{fig:b2dnt}
    }
  \end{figure}
%-----------------------------------------------------------------------------

@@

%-----------------------------------------------------------------------------
  \begin{figure*}[h]
  \centering
  \hspace{-1.25cm}
  \includegraphics[width=0.3965\linewidth]{fig/b310c.png}\hspace{-1.15cm}
  \includegraphics[width=0.3965\linewidth]{fig/b310w.png}\hspace{-1.15cm}
  \includegraphics[width=0.3965\linewidth]{fig/b310h.png}
  \hspace{-1.25cm}
  \caption[Volume snapshots of $\vect{B}$ by phase for Model~$\Ompa$]{
  Vector plots of the magnetic field $\vect{B}$ {\text{(a)}} in the cold phase
  {\text{(b)}} the warm phase and {\text{(c)}} the hot phase.
  Field directions are indicated by arrows and strength by their thickness.
  The colour of the arrows indicates the strength of the
  azimuthal ($y$) component (colour bar on the right).
  The background shading illustrates the density of the ISM.
  \label{fig:b3box}}
  \end{figure*}
%-----------------------------------------------------------------------------

>>>>

  The total volume probability distributions for gas number density $n$, 
  temperature $T$ and thermal pressure $p$ are displayed in Fig.~\ref{fig:pdfm}
  from Models~$\Ompa$ (black, solid) and $\Omph$ (blue, dashed). 
%  Note that Model~$\Omph$ includes the correction to the SN distribution,
%  which stabilises the disc against unphysical cyclic oscillations, although
%  it is still subject to natural random vertical fluctuations.
%  Hence the mean density in the SN active region remains consistently higher
%  than in Model~\Op.
%-----------------------------------------------------------------------------
  \begin{figure}
  \centering
  \includegraphics[width=0.9\columnwidth,clip=true,trim=0 0 0 9mm]{fig/o1pr_rpdf.png}
  \includegraphics[width=0.9\columnwidth,clip=true,trim=0 0 0 9mm]{fig/o1pr_tpdf.png}
  \includegraphics[width=0.9\columnwidth,clip=true,trim=0 0 0 9mm]{fig/o1pr_ppdf.png}
    \caption[Total volume probability distributions for Model~$\Ompa$ and $\Omph$]{
  Volume weighted probability distributions of gas number
  density~{\textbf{(a)}}, temperature~{\textbf{(b)}} and thermal
  pressure~{\textbf{(c)}} for  models {$\Omph$} (black, solid) and
  {$\Ompa$} (blue, dashed) for the total numerical domain $|z|\le1.12\kpc$.
    \label{fig:pdfm}}
  \end{figure}
%-----------------------------------------------------------------------------
  A three phase temperature distribution is visible for Model~$\Omph$ (HD)
  model in Fig.~\ref{fig:pdfm}b, while less apparent for Model~$\Ompa$ (MHD),
  with a significantly narrower range of temperatures.
  The bulk of the density distributions (a) are quite similar between the 
  HD and MHD model, except that the high densities are not as well resolved in
  the MHD model.
  The thermal pressure distributions are very similar, but with the HD modal
  pressure approximately one third the MHD modal pressure. 
  \footnote{FAG: I think these plots are averages of several snapshots in the 
  kinematic dynamo -- need to check -- while the analysis elsewhere is on the 
  saturated field}
  Even with a relatively weak magnetic field, there is significantly increased
  stiffness to the ISM, which restricts transport of the hot gas away from the
  disk (FAG: Kompaneets?), and may also act as a break on the supersonic
  flows, reducing the material collected in the snowplough phase of the SN and
  hence less cold gas resolved in the model (FAG: cite?)
%-----------------------------------------------------------------------------
  \begin{figure}
  \centering
  \includegraphics[width=0.9\columnwidth]{fig/zrhom.png}
  \includegraphics[width=0.9\columnwidth]{fig/zrppm.png}
    \caption[Horizontal averages of $n$ and $P$ for Model~$\Ompa$ and $\Omph$]{
  Horizontal averages of gas number density, $\mean{n}(z)$ {\textbf{(a)}}, and
  total pressure, $\mean{P}(z)$ {\textbf{(b)}}, for Model~{$\Ompa$} (solid,
  black), and Model~{$\Omph$} (dashed, blue). 
  Each are time-averaged using eleven snapshots respectively, spanning 
  100\Myr.
  The vertical lines indicate standard deviation within each horizontal slice.
  The thermal $\mean{p}(z)$ (dotted) and ram $\mean{p}\turb(z)$ (fine dashed)
  pressures are also plotted {\textbf{(b)}}.
%  For Model~{\OpH} the magnetic pressure $\mean{p}_B$ is also plotted (fine, 
%  dash-3dotted).
    \label{fig:zrhom}
            }
  \end{figure}
%-----------------------------------------------------------------------------

%  As discussed in Section~\ref{subsect:params} the stability of the disc
%  reduces the effectiveness of the SNe to generate and circulate hot gas, in
%  the absence of SN clustering. 
%  Hence Model~$\Omph$ has a slightly thicker disc, with less hot gas than 
%  Model~\Op.
  The effect of the magnetic pressure in Model~$\Ompa$ is to 
  expand the thick disc even further and this is illustrated in 
  Fig.~\ref{fig:zrhom}a, where the horizontal averages of gas number density
  $n(z)$ are plotted against $z$ for both models. 
  The strong peak in the density at the mid-plane is evident for Model~$\Omph$
  (black, solid), while for Model~$\Ompa$ (blue, dashed) there is a broad
  plateau in the density, extending to $|z|\simeq300\pc$, where the mean 
  magnetic field is strongest.

%-----------------------------------------------------------------------------
  \begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/o1pr_npdf3s.png}  
  \includegraphics[width=0.9\linewidth]{fig/o1ph_npdf3s.png}\\  
  \includegraphics[width=0.9\linewidth]{fig/o1pr_tpdf3s.png}
  \includegraphics[width=0.9\linewidth]{fig/o1ph_tpdf3s.png}  
    \caption[Probability distributions by phase for $n$ and $T$]{
  Probability distributions by phase: cold (blue, dashed), warm (black, solid)
  and hot (red, dash-dotted) for gas number density ($n$ {\textbf{(a), (b)}})
  and temperature ($T$ {\textbf{(c), (d)}}) 
  for Model~$\Ompa$ ({\textbf{(a), (c)}}) and Model~$\Omph$
  ({\textbf{(b), (d)}}).
%  Data are averaged over 100\,Myr using eleven snapshots. 
  95\% confidence intervals for temporal deviation are shown as error bars.   
  \label{fig:npdf3s}
    }
  \end{figure}
%-----------------------------------------------------------------------------

  The horizontal averages of the pressure are plotted in Fig.~\ref{fig:zrhom}b
  for both models. 
  There is a strong peak at the mid-plane in the turbulent pressure for the HD
  model (black, dashed), but a much weaker profile for the MHD model (blue,
  dash-dotted). 
  There are two peaks in the magnetic pressure (blue, dash-3dotted) near 
  $|z|\simeq200\pc$, which supports the extended density profile.
  Another possible effect, which might constrain the circulation of the hot
  gas, and hence enhance the pressure at the mid-plane, is the strong 
  horizontal orientation of the field.
  The periodic boundary conditions
  exclude a non-zero vertical component to the mean field, so the magnetic
  tension predominantly acts against the vertical flows.
  Some understanding of the multi-phase structure of the magnetised ISM is
  still possible from these models, but the extreme temperatures and densities
  are significantly under represented.
  To improve this in future work it will be desirable to allow unrestricted 
  evolution of vertical field and to apply realistic clustering of the 
  SNe to generate more supperbubbles (composite multiple SN remnants forming a
  single superstructure) or chimneys (plumes venting hot gas from the disc 
  towards the halo).

  Results for separation of the ISM into three phases using the method 
  detailed in \cite[][Ch. 5.3]{Gent12} are shown for Models~$\Ompa$ and
  $\Omph$ in Fig~\ref{fig:npdf3s} with total volume probability distributions.
  The phases are defined using entropy $s$ such that for cold 
  $s<4.4\cdot10^{8}\erg \g^{-1}\K^{-1}$ and hot 
  $s>23.2\cdot10^{8}\erg \g^{-1}\K^{-1}$ with warm in between.
  Apart from the higher densities for the cold phase with the HD model (panel 
  b), 
  anticipated by the volume distributions (Fig.~\ref{fig:pdfm}), the warm and
  hot distributions for the MHD density (panel a) are broad, with a bimodal 
  structure to the hot gas. 
  The distributions for the warm gas (panels c and d) are very similar and for
  the cold (hot) distributions the MHD model does not extend to as low (high)
  temperatures.

%-----------------------------------------------------------------------------
  \begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/o1pr_pdf2dtn.png}  
  \includegraphics[width=0.9\linewidth]{fig/o1ph_pdf2dtn.png}
    \caption[2D probability distribution of $n$ and $T$ for Models~$\Ompa$ and $\Omph$]{
  Probability contour plot by volume of log$n$ vs log$T$ for Model~$\Ompa$
  {\textbf{(a)}}
  and Model~$\Omph$ {\textbf{(b)}}.
  The lines of constant entropy $s=4.4\cdot10^{8}$ 
  and $23.2\cdot10^{8}\erg\g^{-1}\K^{-1}$ indicate where the phases are defined
  as cold for $s\le4.4$ and as hot for $s>23.2$. 
  \label{fig:b2dv}
    }
  \end{figure}
%-----------------------------------------------------------------------------

  Comparing the combined probability distribution of density and temperature
  for both of these models in Fig.~\ref{fig:b2dv} with those of Model~\Op\
  in \cite[][Fig. 5.10]{Gent12} the spread is more broad and not obviously 
  aligned along a line of constant pressure.
  The HD distribution here is less compact than with MHD. 
  However when considering only the mid-plane distributions, as displayed in
  Fig.~\ref{fig:b2dh} the distributions match better with Model~\Op\ and the 
  pressure alignment is evident.
  So the broad distributions for the total volumes are explained by the 
  stronger gradient in the pressure distribution, due to the reduced 
  stirring of the hot gas.
  The thermal pressure at the mid-plane is also very similar in both models,
  reflected also in the agreement of the total and thermal pressure near the
  mid-plane in the plot of horizontal averages (Fig~\ref{fig:zrhom}b).
  The magnetic and turbulent pressure in Model~$\Ompa$ combine to match the
  mid-plane turbulent pressure alone of Model~$\Omph$.
  For the temperature in Model~$\Ompa$ the hot gas has two modes, evident in 
  Fig.~\ref{fig:b2dv}a at $10^5\K$ and $10^6\K$, but at the mid-plane there 
  only the single $10^3\K$ mode. 
  The structure of the ISM at the mid-plane is therefore common to both models
  with modes at $10^6\K,~10^{-2}\cmcube$ and $10^4\K,~1\cmcube$.
  The cold gas is insufficiently resolved in Model~$\Ompa$ for comparison.

%-----------------------------------------------------------------------------
  \begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/o1pr_pdf2dh.png}  
  \includegraphics[width=0.9\linewidth]{fig/o1ph_pdf2dh.png}
    \caption[2D mid-plane probability distribution for Models~$\Ompa$ and  $\Omph$]{
  The mid-plane probability distributions ($|z|<100\pc$) by gas number density 
  $\log n$ and temperature $\log T$ for {\textbf{(a)}} Model~$\Ompa$ and
  {\textbf{(b)}} Model~$\Omph$.
  \label{fig:b2dh}
    }
  \end{figure}
%-----------------------------------------------------------------------------

@@

%-----------------------------------------------------------------------------
  \begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/o1pr_pdf2db.png}  
  \includegraphics[width=0.9\linewidth]{fig/o1pr_pdf2tb.png}
    \caption[2D probability distribution of $n,B$ and $B,T$ for Model~$\Ompa$]{
  Total volume probability distributions ($|z|<100\pc$) by gas number density 
  $\log n$ and magnetic field strength $\log |B|$ {\textbf{(a)}} and
  temperature $\log |T|$ and magnetic field strength $\log |B|$ 
  {\textbf{(b)}} for Model~$\Ompa$.
  \label{fig:b2dnt}
    }
  \end{figure}
%-----------------------------------------------------------------------------

@@

%-----------------------------------------------------------------------------
  \begin{figure*}
  \centering
  \hspace{-1.25cm}
  \includegraphics[width=0.35\linewidth]{fig/b310c.png}\hspace{-1.15cm}
  \includegraphics[width=0.35\linewidth]{fig/b310w.png}\hspace{-1.15cm}
  \includegraphics[width=0.35\linewidth]{fig/b310h.png}
  \hspace{-1.25cm}
  \caption[Volume snapshots of $\vect{B}$ by phase for Model~$\Ompa$]{
  Vector plots of the magnetic field $\vect{B}$ {\text{(a)}} in the cold phase
  {\text{(b)}} the warm phase and {\text{(c)}} the hot phase.
  Field directions are indicated by arrows and strength by their thickness.
  The colour of the arrows indicates the strength of the
  azimuthal ($y$) component (colour bar on the right).
  The background shading illustrates the density of the ISM.
  \label{fig:b3box}}
  \end{figure*}
%-----------------------------------------------------------------------------

### 2015-01-11 field_lines/paper.tex

\documentclass[useAMS,usenatbib]{mn2e}
%FAG added header file to contain macros
\include{header}
%\usepackage{amsmath}
%\usepackage{bm}
%\usepackage{mathtools}
%\usepackage{graphicx,subfigure}
%\usepackage{caption}
%\usepackage{varioref}
%\usepackage{float}
%\restylefloat{table}
% If your system does not have the AMS fonts version 2.0 installed, then
% remove the useAMS option.
%
% useAMS allows you to obtain upright Greek characters.
% e.g. \umu, \upi etc.  See the section on "Upright Greek characters" in
% this guide for further information.
%
% If you are using AMS 2.0 fonts, bold math letters/symbols are available
% at a larger range of sizes for NFSS release 1 and 2 (using \boldmath or
% preferably \bmath).
%
% The usenatbib command allows the use of Patrick Daly's natbib.sty for
% cross-referencing.
%
% If you wish to typeset the paper in Times font (if you do not have the
% PostScript Type 1 Computer Modern fonts you will need to do this to get
% smoother fonts in a PDF file) then uncomment the next line
% \usepackage{Times}

@@

\include{mhdruns}

@@

\begin{figure}[h]

@@

\section{Conclusions}

>>>>

\documentclass[useAMS,usenatbib]{mn2e}
%FAG added header file to contain macros
\input{header}
%\usepackage{amsmath}
%\usepackage{bm}
%\usepackage{mathtools}
%\usepackage{graphicx,subfigure}
%\usepackage{caption}
%\usepackage{varioref}
%\usepackage{float}
%\restylefloat{table}
% If your system does not have the AMS fonts version 2.0 installed, then
% remove the useAMS option.
%
% useAMS allows you to obtain upright Greek characters.
% e.g. \umu, \upi etc.  See the section on "Upright Greek characters" in
% this guide for further information.
%
% If you are using AMS 2.0 fonts, bold math letters/symbols are available
% at a larger range of sizes for NFSS release 1 and 2 (using \boldmath or
% preferably \bmath).
%
% The usenatbib command allows the use of Patrick Daly's natbib.sty for
% cross-referencing.
%
% If you wish to typeset the paper in Times font (if you do not have the
% PostScript Type 1 Computer Modern fonts you will need to do this to get
% smoother fonts in a PDF file) then uncomment the next line
% \usepackage{Times}

@@

\input{mhdruns}

@@

@@

\section{Conclusions}
%FAG
Note, that the mean magnetic field is strongest in the warm phase and the 
dynamo is strongest in the SN dense region within 500\pc of the midplane. 
These results support the hypothesis that the mean field is closely aligned to 
the warm phase of the ISM.
The fluctuating magnetic field is present in similar magnitude in all phases.
Note, in the warm phase, away from the midplane the magnetic field has a 
stronger vertical component, even though in these models the periodic boundary
conditions constrain the net $B_z$ to be zero on each horizontal slice. 
Given more open horizontal boundaries, we could anticipate the mean field 
actually to exhibit more vertical structure. 
With higher numerical diffusion required for the hot gas, the fluctuation 
dynamo in this phase may have been relatively suppressed, although the 
Reynolds numbers may have been higher than in the warm gas as both the length
scales and the velocities of the turbulence are tyically higher in the hot gas
than in the warm.
Nevertheless, a higher resolution run would be helpful in assessing how robust
is the alignment of the mean field to the warm phase, and whether the
fluctuating field in the hot phase may yet have relatively greater amplitude
than obtained here.
Given the dominance of the dynamo about the midplane, this may be feasible
without extending the domain vertically.
